---
output: github_document
editor_options: 
  chunk_output_type: console
---

[![Travis-CI Build Status](https://travis-ci.org/mdsumner/cconvention.svg?branch=master)](https://travis-ci.org/mdsumner/cconvention)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/mdsumner/cconvention?branch=master&svg=true)](https://ci.appveyor.com/project/mdsumner/cconvention)
[![Coverage Status](https://img.shields.io/codecov/c/github/mdsumner/cconvention/master.svg)](https://codecov.io/github/mdsumner/cconvention?branch=master)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# cconvention

The goal of cconvention is to provide access to the CCAMLR convention in spatial form, from scratch. 
 

## Installation

You can install cconvention from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("mdsumner/cconvention")
```

## Work in progress

This project aims to collate the agreed boundaries define by CCAMLR. 

* The `division` functions shows a manual way of doing this, encoding the path steps taken to define boundary lines
* the `parse-text` vignette uses `Combin8R` to begin building an automated tool for extracting the information from the text

Either method results in a 1D topology, the connected boundaries in raw geographic space that need to 
be "baked-in", both by introducing intermediate vertices to carry curvature and to integrate implicit physical boundaries specied in the text, such as "coastline" or "ice shelf". 

After baking, we can provide easy to use map structures for analytical work. The main advantage to using this process is to avoid artefacts introduced by inexact geo-spatial operations. 

## Example

This is a basic example which loads an in-built data set. 

```{r example}
library(cconvention)
subarea <- division()

library(sp)
library(rgdal)
p <- spTransform(subarea, "+proj=laea +lon_0=147 +lat_0=-90 +ellps=WGS84 +no_defs")
plot(p, col = "darkgrey")


```

```{r s48}
SOmap::SOmap()
for (i in seq(48.1, 48.6, by = 0.1)) {
  SOplot(division(i))
}

```
